Geometric variational problems

### 2020-11-10 NSF2020/Description/specificaim1_ver2.tex
rjr

\begin{figure}
  \centering{\includegraphics[width=0.80\textwidth]{Figures/Deformations.pdf}}
  \caption{
    }
\end{figure}

@@

To evaluate $\KG$, we will combine the string method from PI-Ryham's work on fusion \cite{RyKlYaCo16} with
the present particle simulations. The string method is a numerical scheme that finds
least energy pathways separating energy basins \cite{doi:10.1063/1.2720838}.
Using the string method, we will evaluate the transition energies between the intact pancake shape,
and one with a pore. Pore formation in a single bilayer decreases the integral of saddle splay from $4\pi$
to $0$. We can, in principle, detect this drop in energy because we have already accounted for the other deformations.

We will also analyze $\KG$ using a helical geometry. In a helicoid with inclination $m$, the director
gradient is $\nabla n = \begin{pmatrix} 0 & m(m^2+x_1^2)^{-1} \\ m(m^2+x_1^2)^{-1} & 0\end{pmatrix}$ where $x_1$ is the distance to the central
axis. We observe that saddle splay, twist and tilt are zeros, and $\det \nabla n = m^2(m^2+x_1^2)^{-2}$.
In the simulations, the particles forming the helicoid will be confined to two, concentric cylinders. The
continuum energy $\tfrac{1}{2}\KG h(m x_1(m^2+x_1^2)^{-1} + \tan^{-1}(x_1/m)) |_{r_1}^{r_2}$ where $h$, $r_1$ and $r_2$
are the cylinder heights, inner cylinder radius, and outer cylinder radius, respectively.

>>>>

\begin{figure}
  \centering{\includegraphics[width=0.80\textwidth]{Figures/Deformations.pdf}}
  \caption{\label{fig:deformations}
    }
\end{figure}

@@

\begin{wrapfigure}[16]{r}{0.32\textwidth}
\centerline{\includegraphics[width=0.32\textwidth]{Figures/SaddleSplayDiagram.pdf}}
\caption{
\label{fig:saddle_splay}  
 TBD
}
\end{wrapfigure}
To evaluate $\KG$, we will combine the string method from PI-Ryham's work on fusion \cite{RyKlYaCo16} with
the present particle simulations. The string method is a numerical scheme that finds
least energy pathways separating energy basins \cite{doi:10.1063/1.2720838}.
Using the string method, we will evaluate the transition energies between the intact pancake shape,
and one with a pore. Pore formation in a single bilayer decreases the integral of saddle splay from $4\pi$
to $0$. We can, in principle, detect this drop in energy because we have already accounted for the other deformations.

%We will also analyze $\KG$ using a helical geometry. In a helicoid with inclination $m$, the director
%gradient is $\nabla n = \begin{pmatrix} 0 & m(m^2+x_1^2)^{-1} \\ m(m^2+x_1^2)^{-1} & 0\end{pmatrix}$ where $x_1$ is the distance to the central
%axis. We observe that saddle splay, twist and tilt are zeros, and $\det \nabla n = m^2(m^2+x_1^2)^{-2}$.
%In the simulations, the particles forming the helicoid will be confined to two, concentric cylinders. The
%continuum energy $\tfrac{1}{2}\KG h(m x_1(m^2+x_1^2)^{-1} + \tan^{-1}(x_1/m)) |_{r_1}^{r_2}$ where $h$, $r_1$ and $r_2$
%are the cylinder heights, inner cylinder radius, and outer cylinder radius, respectively.
